Create data sets for modeling

### 2016-07-27 portfolio/analysis/3-createData_linear_modeling.Rmd
added new calc for days

if ("VLength" %in% names(cfecnew)) {
  cfecnew <- rename(cfecnew, vlength = VLength)
}
cfecAnnual = group_by(cfecnew, p_holder, year) %>%
  summarize(permit = p_fshy[1], boat = cadfg[1],
    days = diff(range(yday) + 1),
    days_n = length(unique(yday)),
    ngear = length(unique(gearn)),
    nspec = length(unique(specn)),
    npermit = length(unique(p_fshy)),
    revenue = sum(g_earn),
    weight = sum(g_pounds),
    length = mean(vlength, na.rm=TRUE),
    strategy = strategy[1],
    strategy_gear = strategy_gear[1])

# also calculate weighted simpson diversity of gears and species
cfecAnnual = left_join(cfecAnnual, group_by(cfecnew, p_holder, year, specn) %>%
  summarize(totRev.spec = sum(g_earn)) %>%
  group_by(p_holder, year) %>%
  summarize(specDiv = simp.div(totRev.spec)))

# also calculate weighted simpson diversity of gears and species
cfecAnnual = left_join(cfecAnnual, group_by(cfecnew, p_holder, year, gearn) %>%
  summarize(totRev.gear = sum(g_earn)) %>%
  group_by(p_holder, year) %>%
  summarize(gearDiv = simp.div(totRev.gear)))

>>>>

if ("VLength" %in% names(cfecnew)) {
  cfecnew <- rename(cfecnew, vlength = VLength)
}

# calculate 
permit_days = group_by(cfecnew, p_holder, year, p_fshy) %>%
  summarize(permitDays = diff(range(yday)+1)) %>%
  group_by(p_holder, year) %>% 
  summarize(tot.permitDays = sum(permitDays))

cfecAnnual = group_by(cfecnew, p_holder, year) %>%
  summarize(permit = p_fshy[1], boat = cadfg[1],
    days = diff(range(yday) + 1),
    days_n = length(unique(yday)),
    ngear = length(unique(gearn)),
    nspec = length(unique(specn)),
    npermit = length(unique(p_fshy)),
    revenue = sum(g_earn),
    weight = sum(g_pounds),
    length = mean(vlength, na.rm=TRUE),
    strategy = strategy[1],
    strategy_gear = strategy_gear[1])

cfecAnnual = left_join(cfecAnnual, permit_days)
# also calculate weighted simpson diversity of species
cfecAnnual = left_join(cfecAnnual, group_by(cfecnew, p_holder, year, specn) %>%
  summarize(totRev.spec = sum(g_earn)) %>%
  group_by(p_holder, year) %>%
  summarize(specDiv = simp.div(totRev.spec)))

# also calculate weighted simpson diversity of gears
cfecAnnual = left_join(cfecAnnual, group_by(cfecnew, p_holder, year, gearn) %>%
  summarize(totRev.gear = sum(g_earn)) %>%
  group_by(p_holder, year) %>%
  summarize(gearDiv = simp.div(totRev.gear)))
